% ATS-oriented résumé: Inter via CTAN `inter` package (bundled OTFs; portable with Tectonic). Rule above each section title.
% For strict \usepackage{fontspec}\setmainfont{Inter}, install Inter system-wide first; otherwise use `inter` below.
% Visual portfolio version: Prajwal_BR_Resume.tex
% Build: tectonic Prajwal_BR_Resume_ATS.tex  (or npm run resume:build)
\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[sfdefault,scaled=0.96]{inter}
\usepackage[margin=0.54in]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{url}

\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  pdfauthor={Prajwal B R},
  pdftitle={Prajwal B R --- Resume (ATS)},
}

\definecolor{Body}{HTML}{222222}
% Secondary text: dark enough for WCAG-like contrast on white and on gray!7/gray!10 panels
\definecolor{metagray}{HTML}{454545}
% Clickable links: thin blue frame (readable on white; PDF still parses as normal links)
\definecolor{LinkBlue}{HTML}{2563EB}
\newlength{\atslinkfsep}
\newlength{\atslinkfrule}
\setlength{\atslinkfsep}{2.6pt}
\setlength{\atslinkfrule}{0.5pt}
\newcommand{\atslinksmall}[2]{%
  \href{#1}{%
    \begingroup
    \small
    \setlength{\fboxsep}{2.4pt}%
    \setlength{\fboxrule}{\atslinkfrule}%
    \fcolorbox{LinkBlue}{white}{\color{Body}#2}%
    \endgroup
  }%
}

\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=1.05em, topsep=0.06em, itemsep=0.05em, parsep=0pt, partopsep=0pt}

% Section: horizontal rule first, then title (premium CV pattern); 10pt before next block
\newcommand{\atsection}[1]{%
  \par\addvspace{10pt}%
  \noindent\rule{\linewidth}{0.6pt}%
  \par\vspace{4pt}%
  {\large\bfseries #1}%
  \par\vspace{6pt}%
}

\newcommand{\thinhrule}{%
  \par\vspace{2pt}\noindent\textcolor{metagray}{\rule{\linewidth}{0.35pt}}\par\vspace{3pt}%
}

\setlength{\fboxsep}{6pt}
% Project card: linked title; metagray tech row ($\cdot$ separators)
\newcommand{\projcard}[3]{%
  \par\vspace{6pt}%
  \noindent\colorbox{gray!10}{%
    \parbox{\dimexpr\linewidth-2\fboxsep\relax}{%
      \href{#2}{%
        \begingroup
        \setlength{\fboxsep}{3pt}%
        \setlength{\fboxrule}{\atslinkfrule}%
        \fcolorbox{LinkBlue}{white}{\large\textbf{\color{Body}#1}}%
        \endgroup
      }\\[2pt]
      {\small\textcolor{metagray}{#3}}%
    }%
  }\par\nobreak\vspace{2pt}%
}
\newcommand{\projpost}{\par\vspace{6pt}}

\newcommand{\subtlehref}[2]{\atslinksmall{#1}{#2}}

\begin{document}
\thispagestyle{empty}
\pagestyle{empty}
\color{Body}

% ---------- Header (exact structure) ----------
\begin{center}
{\Huge\textbf{Prajwal B R}}\\[5pt]
{\large Full-Stack \& AI Developer}\\[7pt]
{\small
Bengaluru, India \quad | \quad
\atslinksmall{mailto:prajwalbr0304@gmail.com}{prajwalbr0304@gmail.com}
\quad | \quad
\atslinksmall{https://github.com/PRAJWAL-BR-0304}{GitHub}
\quad | \quad
\atslinksmall{https://www.linkedin.com/in/prajwal-reddy-34024b307/}{LinkedIn}
\quad | \quad
\atslinksmall{https://prajwalbr.netlify.app}{My Portfolio}
}
\end{center}

% Single rule before first section (avoid double line with \atsection rule)
\vspace{10pt}

% ---------- Summary ----------
\atsection{Summary}
{\small
Full-stack engineer shipping web applications, blockchain-integrated systems, and LLM-powered products using React, Next.js, Django, Supabase, and cloud APIs. Currently an R\&D Engineering Intern at Nokia (OHUB), focused on backend systems, applied AI, API design, and reliable release engineering. Comfortable owning features end-to-end from authentication and API development through deployment, testing, and CI workflows. Public GitHub portfolio includes Web3 platforms, Supabase-backed SaaS applications, RAG-based assistants, and developer-focused AI tools with streamed model responses.
}

% ---------- Education ----------
\atsection{Education}
{\small
B.E.\ Computer Science and Engineering (expected 2026)\\
Dayananda Sagar University, Bengaluru, Karnataka\\
\textcolor{metagray}{CGPA: 8.91 / 10.0}\\[0.25em]
\atslinksmall{https://prajwalbreducation.netlify.app}{Explore Education}
}

% ---------- Experience ----------
\atsection{Experience}

{\small
\noindent\textbf{Nokia}\ \textemdash\ R\&D Engineer Intern\hfill\textcolor{metagray}{\textit{Jul 2025 -- Present}}\par
\noindent\textcolor{metagray}{\textit{Bengaluru (on-site), OHUB}}\par
\vspace{0.06em}
\begin{itemize}
  \item Automated build and regression checks that reduced manual validation cycles for OHUB platform releases.
  \item Delivered internal APIs and backend services integrated with existing Nokia tooling used by R\&D teams.
  \item Expanded unit and integration coverage with reproducible fixtures alongside CI pipeline updates.
\end{itemize}

\thinhrule

\noindent\textbf{Independent Projects}\hfill\textcolor{metagray}{\textit{2023 -- Present}}\par
\vspace{0.06em}
\begin{itemize}
  \item Shipped public full-stack and Web3 repos spanning traceability, auctions, and LLM-backed document flows on GitHub.
  \item MediTrustChain and DeFi-Homes combine web, contracts, and wallet flows; KNOWLEDGE-BASE and AI-GRAMMAR pair Supabase with Groq/OpenAI behind signed-in clients.
  \item Tightened async UI state around model calls and uploads to cut failure modes in deployed demos.
\end{itemize}
}

% ---------- Technical skills ----------
\atsection{Technical skills}
\setlength{\fboxsep}{7pt}
\noindent\colorbox{gray!7}{%
  \parbox{\dimexpr\textwidth-2\fboxsep\relax}{%
    {\small
    \setlength{\parskip}{3pt}
    \textcolor{metagray}{Languages:} Python, TypeScript, JavaScript, Java, C, SQL, HTML/CSS, Solidity, Dart

    \textcolor{metagray}{Frontend:} React, Next.js, Tailwind CSS, Vite

    \textcolor{metagray}{Backend:} Django, Django REST Framework, Flask, Express.js, Node.js, REST APIs, sessions, JWT authentication

    \textcolor{metagray}{Databases:} PostgreSQL, MySQL, MongoDB, Supabase (Auth, RLS-aware clients)

    \textcolor{metagray}{AI/LLM:} OpenAI API, Groq, Gemini API integrations, prompt engineering, RAG, streamed responses in the browser

    \textcolor{metagray}{Web3:} Ethereum/Sepolia, MetaMask, ethers.js, contract-aware front ends, on-chain auctions and provenance tracking

    \textcolor{metagray}{DevOps:} Docker, Git, GitHub, CI/CD, unit and integration tests, Playwright, Selenium

    \textcolor{metagray}{Deployments:} Dockerized services, Render, Vercel, AWS S3 uploads
    }%
  }%
}

% ---------- Publications ----------
\atsection{Publications}
{\small
\setlength{\parskip}{0.3em}

\noindent\textbf{MediTrustChain} --- Blockchain-Based Pharmaceutical Supply Chain Traceability with AI-Assisted Anomaly Detection\\
\textbf{\textit{ICAISE 2026}}, Springer Nature (published) \ \textbar\ \ \subtlehref{https://link.springer.com/chapter/10.1007/978-3-032-23547-3_23}{Springer listing}

\vspace{0.35em}
\noindent\textbf{DefiHomes} --- A Decentralized Real Estate Auction Platform with Transparent On-Chain Bidding\\
\textbf{\textit{ICDMIS 2025}}, Springer Nature LNNS (published) \ \textbar\ \ \subtlehref{https://link.springer.com/book/10.1007/978-3-032-25955-4}{Springer listing}

\vspace{0.35em}
\noindent\textbf{Smart Cradle} --- Secured Assistance and Monitoring System for Babies Using IoT\\
\textbf{\textit{IEEE}} conference publication \ \textbar\ \ \subtlehref{https://ieeexplore.ieee.org/abstract/document/10823361}{IEEE Xplore}
}

% Projects: start on next page so rule + heading stay with cards (avoid orphaned title)
\newpage
% ---------- Projects ----------
\atsection{Projects}
{\small
\projcard{MediTrustChain}{https://github.com/PRAJWAL-BR-0304/MediTrustChain}{Next.js $\cdot$ Solidity (Sepolia) $\cdot$ Supabase $\cdot$ Flutter}
\begin{itemize}
  \item Delivered batch traceability with on-chain provenance and anomaly signals for monitoring teams.
  \item Unified web and Flutter clients on one authenticated backend for regulated workflows.
\end{itemize}
\projpost

\projcard{DeFi-Homes}{https://github.com/PRAJWAL-BR-0304/DeFi-Homes}{React $\cdot$ Vite $\cdot$ Tailwind $\cdot$ Supabase $\cdot$ MetaMask $\cdot$ ethers.js}
\begin{itemize}
  \item Enabled MetaMask-based bidding with Supabase-backed listings and price history charts.
  \item Kept bid history on Ethereum testnets while profiles and inventory stayed in Postgres.
\end{itemize}
\projpost

\projcard{KNOWLEDGE-BASE}{https://github.com/PRAJWAL-BR-0304/KNOWLEDGE-BASE}{React $\cdot$ Vite $\cdot$ Supabase $\cdot$ Groq $\cdot$ Markdown}
\begin{itemize}
  \item Reduced time-to-answer by pairing Groq generation with stored Markdown pages behind Supabase auth.
  \item Improved reliability with structured loading, cancellation, and error handling for model calls.
\end{itemize}
\projpost

\projcard{PDF-to-Text Converter}{https://github.com/PRAJWAL-BR-0304/pdf-to-text-converter}{Python $\cdot$ Flask $\cdot$ OCR.space $\cdot$ Docker}
\begin{itemize}
  \item Automated PDF-to-text extraction with native parsers plus OCR for scans, cutting manual copy-paste by roughly 80\% on mixed document sets.
  \item Packaged a Dockerfile and deployment notes for repeatable cloud or local runs.
\end{itemize}
\projpost

\textcolor{metagray}{Additional:} eden-thought (Django, PostgreSQL, S3, Render), AI-GRAMMAR (Node, Express, EJS, OpenAI), Student-Management-System (Django 5, RBAC) \ \textbar\ \ \subtlehref{https://github.com/PRAJWAL-BR-0304?tab=repositories}{All repositories}
}

% ---------- Certifications ----------
\atsection{Certifications}
{\small
\noindent\textcolor{metagray}{%
Google Cloud, Amazon Bedrock, IBM AI Fundamentals, Django 5, Prompt Engineering, Generative AI (LLM), Infosys Springboard%
}
}

% ---------- Languages ----------
\atsection{Languages}
{\small
English, Kannada, Hindi, Telugu.
}

\end{document}
